---
title: "Group29"
subtitle: "Week3"
author: 
  - Ricky Yuan
thanks: "Code and data are available at: LINK."
date: 9/19
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @Ricky

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: fig-marriage
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

And also planes (@fig-planes). 




# Discussion

## First discussion point {#sec-first-point}
 
The paper should talk about the data details first that reader can know the context in the future.

## Second discussion point
The second paper should discuss the data cleaning that the data should deal with better selected.

## Third discussion point

The third one should talk about the data test that making the data more correct. 
## Weaknesses and next steps

Some data will be selected incorrect that the problem should be avoided. Then, the data should select better and into the next introduction easily.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


